NumLin: Linear Types for Linear Algebra

### 2019-01-11 write-up/paper/paper.tex
Add ORCiDs

\author{Dhruv C.~Makwana}{Unaffiliated \url{dhruvmakwana.com} }{dcm41@cam.ac.uk}{[orcid]}{}

\author{Neelakantan R.~Krishnaswami}{Department of Computer Science and Technology, University of Cambridge, United Kingdom}{nk480@cl.cam.ac.uk}{[orcid]}{}

>>>>

\author{Dhruv C.~Makwana}{Unaffiliated \url{dhruvmakwana.com} }{dcm41@cam.ac.uk}{https://orcid.org/0000-0001-7220-4991}{}

\author{Neelakantan R.~Krishnaswami}{Department of Computer Science and Technology, University of Cambridge, United Kingdom}{nk480@cl.cam.ac.uk}{https://orcid.org/0000-0003-2838-5865}{}
